\section{Introduction}\label{sec:introduction}
\subsection{Background}\label{subsec:background}
With the rise of third-party public cloud services
such as \ac{AWS}~\cite{aws} and Microsoft Azure~\cite{azure},
there is increasing demand for trusted execution where
applications are protected from
attackers with privileged access to the hardware or software.
Modern hardware offer \ac{TEE} technologies,
such as \ac{SGX} in Intel CPUs,
with which trusted execution code and sensitive data
are processed in secure \q{enclaves},
protected at hardware level to prevent access
from other hardware or software layers.

One significant application of \ac{TEE} is the big data industry,
in which confidential user data are processed on cloud servers,
and protection from cloud providers may be necessary
for compliance with privacy regulations such as GDPR~\cite{gdpr}.
However, a significant amount of big data libraries and frameworks are written
using languages that use \ac{JVM} as the runtime,
such as Hadoop~\cite{apachehadoop} and Spark~\cite{apachespark}.
Recently, Uranus~\cite{uranus}, a system for
writing \ac{SGX} applications in Java languages, was released.
It provides a simple interface for interacting with \ac{SGX} in Java,
where users annotate methods with \code{@JECall} and \code{@JOCall}
to move control flow into or out of enclaves.
It is the responsibility of the user to determine the correct positions
for the \code{@JECall} and \code{@JOCall} annotations,
namely the enclave boundary partitioning.
Since \ac{JVM} involves a very different approach compared to native applications
in terms of software development, distribution and execution,
tools designed for native applications are mostly incompatible in \ac{JVM}.

One important question in enclave programming is the choice of an appropriate enclave boundary.
Running the whole application within an \ac{SGX} enclave is undesirable for two reasons.
First, this violates the Principle of Least Privilege,
where the whole application becomes possible attack surface
for adversaries to compromise protected data~\cite{glamdring}.
Second, this implies all memory used by the application
is placed in the enclave memory (the \ac{EPC}),
which is restricted to 100 MB,
the overflow of which results in swap memory mechanism,
leading to significant performance degrade
(\q{1,000X slowdown compared to regular OS paging}~\cite{uranus}).
On the other hand, if the enclave is smaller than necessary,
adversaries can either obtain sensitive data directly or
infer sensitive characteristics of them indirectly.
An enclave boundary is to be selected with high precision to avoid impacts from either side.
Ideally, the enclave boundary shall cover the minimum subset of code
in which sensitive data are processed
such that use of \ac{EPC} is minimized
without resulting in any sensitive data leak.

This project presents \pname{}
\footnote{\q{enclavlow} is a term coined from the words \q{enclave} and \q{flow}.},
an information flow analysis tool
for identifying data leak from enclaves.
The user first wraps sensitive data sources in \code{sourceMarker} and sinks in \code{sinkMarker}.
The tool performs information flow analysis from \code{sourceMarker} variables,
identifying the ways that data from such variables are leaked
to the system outside the executing enclave
without first passing through a \code{sinkMarker} variable.
The tool compiles a report in HTML format
that lists the flow of sensitive data leak
from the source marker to areas accessible by privileged adversaries.

\pname{} is shipped as a Gradle plugin,
providing a Gradle task that
takes the \code{*.class} files compiled in the \code{classes} task
and generates the report for the analysis from those classes.

\subsection{Prior work}\label{subsec:prior-art}
Information flow analysis is not a new technology in the field.
While this project analyzes \ac{JVM} code using \ac{SGX} enclaves,
prior research on \emph{automatic partition} and non-SGX dynamic analysis was found.

Glamdring~\cite{glamdring} is a C framework that
automatically selects the minimal \ac{SGX} enclave boundaries
based on user requirements specified through C pragma directives.
However, since the process is fully automated,
it has a lower tolerance of false positives,
which increases the risk of unintentional data leak.
This project, unlike Glamdring, will only perform analysis but not automatic partitioning,
allowing for greater false positive tolerance.

Phosphor~\cite{BellJonathan2014Pidd} is a \ac{DTA} framework
that modifies Java bytecode to add tags to sensitive data at runtime
and check if such tags are leaked.
Although dynamic taint is more accurate,
this project prefers a static analysis approach,
which enables developers to identify sensitive regions at compile time
without the need to feed concrete data into methods.

Civet~\cite{civet} is a framework for Java code partitioning.
Similar to Glamdring, it automatically selects the minimal enclave boundaries.
It is also similar to the goal of this project,
except that Uranus provides additional protection at the native level,
allowing further optimizations compared to Civet.
Challenges found in this project, such as polymorphism complexity, were also observed with Civet.

This report will focus on the algorithm used to detect data leaks,
as well as performance concerns and limitations from the \ac{JVM} design.
An example application is evaluated to demonstrate the functionality of \pname{}.
