\section{Methodology}\label{sec:methodology}
The main component of this project is the analysis framework,
which is conducted in the form of iterations
to fulfill security policies as specified in the integration tests.
Other parts such as Gradle plugin interfae,
although necessary for usage,
are not focus areas of this project, and hence will not be discussed further.

\input{methodology-design}

\subsection{Implementation details}\label{subsec:details}
Local and contract flow graphs are considered "dense" graphs,
and are represented using edge matrix.
Meanwhile, the aggregate flow graph has a much lower density of edges,
and an edge list is much more memory-efficient.

Since Soot uses \ac{LFG} equality as the predicate
to decide whether loops have to be analyzed again,
to avoid infinite loops, \fnname{Control} nodes and function calls
are excluded from consideration when comparing the graph.

\subsection{System Requirements}\label{subsec:system-requirements}
The logical code of this project is mostly implemented in Kotlin,
a \ac{JVM} language with more concise syntax than Java.
However, to ensure that the behaviour analyzed
is as explicit as possible,
all test cases are written in Java.

As Uranus was only tested against Linux systems,
this project does not intend to support other operating systems.
Furthermore, due to challenges with classpath detection,
only OpenJDK Versions 8 and 11 are supported currently.
Nevertheless, since \pname{} is just a developer tool,
its runtime is actually independent of that targeted by Uranus,
so it is possible to test support for other platforms in the future.

\pname{} is packaged as a Gradle plugin,
allowing developers to use it in projects with a Gradle toolchain.
However, the \code{enclavlow-core} subproject can be reused in other contexts,
such as Maven plugins, IDE plugins, etc.
With Kotlin toolchain integrated,
it is possible to include enclavlow code into Uranus for compile-time analysis.

\subsection{Flow analysis framework}\label{subsec:flow-analysis-framework}
Soot~\cite{sootsurvivor} was selected as the framework for conducting flow analysis.
Although multiple flow analysis systems using Soot already exist,
they are not designed against \ac{SGX} enclave protection.
\pname{} adopts more strict security policies
to prevent attacks from more privileged attackers,
unlike traditional information flow analysis
that mostly detects user input as the source of insecurity.

Soot accepts Java bytecode files (\code{*.class}) as input
and compiles them into Jimple \ac{3AC},
so inputs compiled from different \ac{JVM} languages are still compatible.
Nevertheless, some languages generate a lot of boilerplate code,
such as null assertion code from Kotlin,
which reduces readability of the report.

Other flow analysis frameworks were also considered,
such as Joana~\cite{joana} and JFlow~\cite{jflow}.
Soot was chosen due to its distinctively thorough documentation
and builtin support for call graph analysis.

\subsection{Testing}\label{subsec:testing}
This project uses JUnit 5 and \code{kotlin.test} framework
to conduct unit tests.
Test case classes are compiled together in the \code{:core:testClasses} task,
which declares dependency on the APIs \code{sourceMarker} and \code{sinkMarker},
but this is not necessary for actual usage.
